Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election

### 2024-03-16 paper/us_election_2020.qmd
some edit

3. region: the census region where the respondent lives; numeric numbers starting from 1 correspond to options "Northeast", "Midwest", "South", and "West", respectively.

4. race: the racial or ethnic group of the respondent; numeric numbers starting from 1 correspond to options "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other", respectively.

@@

We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm. We use the default priors from `rstanarm`. Rstanarm employs Markov chain Monte Carlo (MCMC) techniques to estimate the posterior distribution of the parameters. To avoid exessive runtime, we randomly sampled 1000 observations to fit the model. Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see -@sec-model-details).

@@

More detailed explanation of each plot can be found in -@sec-model-details.

@@

Our discussion is made based on @tbl-modelresults1 from our model, as well as background information on different presidential candidates and their different views of the world and divergent approaches to tackling some of the  issues in the United States.

>>>>

3. race: the racial or ethnic group of the respondent; numeric numbers starting from 1 correspond to options "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other", respectively.

4. region: the census region where the respondent lives; numeric numbers starting from 1 correspond to options "Northeast", "Midwest", "South", and "West", respectively.

@@

We run the model in R [@citeR] using the `rstanarm` package of @citeRstanarm. We use the default priors from `rstanarm`. Rstanarm employs Markov chain Monte Carlo (MCMC) techniques to estimate the posterior distribution of the parameters. To avoid exessive runtime, we randomly sampled 1000 observations to fit the model. Model diagnostics, including convergence checks and posterior summaries, are available in the supplementary materials (see Appendix @sec-model-details).

@@

More detailed explanation of each plot can be found in Appendix @sec-model-details.

@@

Our discussion is made primarily based on the logistic regression model and its result in @tbl-modelresults1, as well as background information on different presidential candidates and their different views of the world and divergent approaches to tackling some of the  issues in the United States.
